RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-27 discussion.tex
yes

Experience with deploying RCloud in a community of data analysts
has provided some insight into how well the proposed requirements
were met and matched their work. This may be informative to
researchers and designers of future systems supporting visual analytics.

Returning to the design considerations outlined by Heer and Agrawala,
our experience underscores the value of several of their proposals,
and suggests areas for further exploration.

{\bf Shared artifacts and artifact histories} are a central feature
of RCloud. The prototype aimed at making it convenient to collaborate
on code and experiments with data. It was a success to observe that analysts
readily shared ideas through RCloud. We noticed them creating experiments
in workbooks and sharing URLs to discuss analysis and programming
problems, instead of sending screenshots in PowerPoint.\todo{Talk about artifact histories?}

{\bf View sharing, bookmarking.} Almost everything in RCloud is named
and accessed as a URL. This proved to be an effective mechanism
for sharing, and for analyses in notebooks to be integrated with
external processes and systems.

>>>>

Experience with deploying RCloud in a community of data analysts
has provided some insight into how well the proposed requirements
were met and were appropriate to the tasks in their work.
This experience may be informative to researchers and designers
of future systems supporting collaborative visual analytics.

Returning to the design considerations defined by Heer and Agrawala,
our experience underscores the value of many of their proposals,
and indicates areas for further exploration.

{\bf Shared artifacts and artifact histories} are a central feature
of RCloud. The prototype aimed at making it convenient to collaborate
on experimental workbooks and the analyses that result. We observed
that analysts readily shared ideas through RCloud. 
creating experiments
in workbooks and sharing URLs to discuss analysis and programming
problems, instead of sending screenshots in PowerPoint.\todo{Talk about artifact histories?}

{\bf View sharing, bookmarking.} Most resources in RCloud are named
and accessed as URLs. This proved to be an effective mechanism
for sharing, and for analyses to be integrated with
external processes and systems.
